---
title: "agrammon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{agrammon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(agrammon)
```

# Title

link to Agrammon REST API: https://redocly.github.io/redoc/?url=https://model.agrammon.ch/single/api/v1/openapi.yaml

## Introduction

This package supports users in using the n-flow(?) model Agrammon (link!) via its REST API interface with the help of R.
It provides 4 functions (list here..) that facilitate
- storing the access token (should it?) (register_token)
- generating a valid data set (a CSV file) containing all necessary input data (save_template)
- running Agrammon via its REST interface (run_agrammon)
- saving results as excel file (save_excel)

- prepare input data set (CSV file)
    - save template
- call model
    - check input data set
    - print data set summary
    - call Agrammon via REST interface
    - check result
- store result
    - save result to Excel file

## Agrammon REST API

- explain rest
- explain package workflow
- access token

## Input Data Set

- create template
- load example data set? and show instances etc.?

## Run Agrammon

- run different example data sets
    - 3 farms ok
    - 1 farm without farm id?
    - ...
